Scikit-learn: machine learning without learning the machinery

### 2014-06-30 article.tex
Finish?

Scikit-learn has become a reference machine learning toolkit. As such, it
should offer a wide variety of learning algorithms. However, each new
feature, each new line of code comes with a significant maintenance cost.
Uncontrolled growth would lead the project to pick up weight until it
comes to a crawl. The difficulty lies in defining the project scope and
prioritizing methods. We strive to integrate all classical methods that
are most useful for prediction tasks. We favor time-tested algorithm and
put great care in the choice of default parameters.

We have found that implementing, even a standard algorithm, really well,
can require a lot of domain knowledge. Thus it is natural that specific
libraries span up to solve it. Some adopt scikit-learn API and standard,
and we hope that scikit-learn has a structural effect on the environment.

Impact on education (documentation)

>>>>

Scikit-learn has become a reference machine learning toolkit. As such, it
should offer a wide variety of learning algorithms. However, each new
feature, each new line of code comes with a significant maintenance cost.
Uncontrolled growth would lead the project to pick up weight until it
comes to a crawl. The difficulty lies in defining the project scope and
prioritizing methods. We strive to identify and integrate all major
methods that are most useful for prediction tasks. We favor time-tested
algorithms and put great care in the choice of default parameters. Our
secret ambition is that the documentation, that we strive to make
didactic and pragmatic, can provide an executable alternative to
textbooks, as all the figures are generated with code examples.

%We have found that implementing, even a standard algorithm, really well,
%can require a lot of domain knowledge. Thus it is natural that specific
%libraries span up to solve it. Some adopt scikit-learn API and standard,
%and we hope that scikit-learn has a structural effect on the environment.
